Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
Consistency with other tables

% \comment{If test scores have the same ranges, we could include a mini table of means and standard deviations of the four tests, and discuss whether these findings are consistent to how people usually score (except for the females we have about the same population).}
\begin{savenotes}
\begin{table}[ht]
\centering
\begin{tabular}{rlll}
  & Card Rotation & Paper Folding & Figure Classification \\\hline
ISU Students & \Sexpr{round(mean(ans.summary.unscaled$card_rot), 2)} (\Sexpr{round(sd(ans.summary.unscaled$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary.unscaled$folding), 2)} (\Sexpr{round(sd(ans.summary.unscaled$folding), 1)})
             & \Sexpr{round(mean(ans.summary.unscaled$fig_class), 2)} (\Sexpr{round(sd(ans.summary.unscaled$fig_class), 1)})\footnote{ISU students took only Part I due to time constraints.}\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 2)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617/2), 1)})\footnote{Averages calculated assuming 294 males and 323 females.}\\
Unscaled Scores & 44.0 (24.6)\footnote{Data from Part I only.}
                & 13.8 (4.5)
                & M:~120.0~(30.0), F:~114.9~(27.8)\\
{\footnotesize Population}    
              & \parbox[t]{.2\textwidth}{\footnotesize $\approx$ 550 male Naval recruits} 
              & \parbox[t]{.2\textwidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.3\textwidth}{\footnotesize Suburban 11-12th grade students\\(288-300 males, 317-329 females)}\\\hline
\end{tabular}

>>>>

% \comment{If test scores have the same ranges, we could include a mini table of means and standard deviations of the four tests, and discuss whether these findings are consistent to how people usually score (except for the females we have about the same population).}
\begin{savenotes}
\begin{table}[ht]
\centering
\begin{tabular}{rlll}
\hline
  & Card Rotation & Paper Folding & Figure Classification \\\hline
ISU Students & \Sexpr{round(mean(ans.summary.unscaled$card_rot), 2)} (\Sexpr{round(sd(ans.summary.unscaled$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary.unscaled$folding), 2)} (\Sexpr{round(sd(ans.summary.unscaled$folding), 1)})
             & \Sexpr{round(mean(ans.summary.unscaled$fig_class), 2)} (\Sexpr{round(sd(ans.summary.unscaled$fig_class), 1)})\footnote{ISU students took only Part I due to time constraints.}\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 2)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617/2), 1)})\footnote{Averages calculated assuming 294 males and 323 females.}\\
Unscaled Scores & 44.0 (24.6)\footnote{Data from Part I only.}
                & 13.8 (4.5)
                & M:~120.0~(30.0), F:~114.9~(27.8)\\
{\footnotesize Population}    
              & \parbox[t]{.2\textwidth}{\footnotesize $\approx$ 550 male Naval recruits} 
              & \parbox[t]{.2\textwidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.3\textwidth}{\footnotesize Suburban 11-12th grade students\\(288-300 males, 317-329 females)}\\\hline
\end{tabular}
